Towards Compiler-Agnostic Performance in Finite-Difference Codes. (TBC)

### 2014-11-11 docs/papers/shallow_performance/shallow_perf.tex
Add list of transformations that have been applied to the code

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

We have results for the Gnu, Intel, Cray and IBM compilers.
We've run on Intel Ivy Bridge, Intel Haswell, and IBM BG/Q.

>>>>

\subsection{The {PS}y{KA}l Approach}
Proliferation of lightweight cores is resulting in increased
complexity in the programming models required to achieve performance.
Combine with the complexity of e.g. a model simulating circulation in
the global ocean. Significant challenge in software engineering.
Propose an approach for meeting this challenge by separating the
computational science demands from the e.g. oceanographic demands.

\begin{figure}
\centering
\caption{The {PS}y{KA}l Approach.}
\end{figure}

While encapsulation makes it easier to produce more robust software,
it can often come with a performance penalty. In this work we
investigate in detail the hardware and compiler dependencies of this
penalty and the steps required to remove it.

@@

We have results for the Gnu, Intel, Cray and IBM compilers.
We've run on Intel Ivy Bridge, Intel Haswell, IBM BG/Q, IBM P8.

\begin{itemize}

\item Performance of the 'original' version of shallow; i.e. the version we
were supplied with at the start of this work.

\item Performance of the vanilla, unoptimised version after it has been
re-structured following the {PS}y{KA}l approach.

\end{itemize}

Beginning with the vanilla {PS}y{KA}l version, we apply a series of
optimisations with the aim of recovering, as much as is possible, the
structure and thus performance of the original version of the code.

\begin{enumerate}

\item Pass explicit array bounds to middle layer (rather than using
  assumed-size array arguments)

\item Move kernel routines into same module as middle layer

\item Loop fusion

\item In-lined field-copy operation

\item Fused field-copy operation

\end{enumerate}

These optimisations do not always result in improved performance (AND
HENCE WE SHOULD CALL THEM TRANSFORMATIONS PERHAPS?). Whether or not
they do so depends both on the compiler and the problem size.
